### 2024-12-09 manuscript.tex
Addressing comments

The Southern Ocean (SO) is known to be a problematic region for climate model
biases due to a lack of surface and in situ observations and being a lower
priority region for numerical weather prediction (NWP) and climate model
development because of its distance from populated areas.  Nevertheless,
radiation biases and changes over an area of its size have a substantial
influence on the global climate, such as affecting the Earth radiation balance
and carbon cycle, and the SO is an important part of the global ocean conveyor
belt. In general, marine clouds have a disproportionate effect on top of
atmosphere (TOA) SW radiation due to the relatively low albedo of the sea
surface.  The relative longitudinal symmetry of the SO means that model cloud
biases tend to be similar across longitudes.  Here, we conventionally refer to
the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and
high-latitude SO as south of 55°S. The reason for this dividing latitude
is to split the SO into about two equal zones, as well as the results by
\cite{schuddeboom2021} (Fig. 2b), showing a contrast in CMIP model radiation
biases, \citep{schuddeboom2019} (Fig. 2) and \cite{kuma2020} (Fig. 3) showing
contrasting radiation biases in the Hadley Centre Global Environmental Model
between these two zones. The findings of \cite{niu2024}, however, support a
different dividing line of 62º based on cloud condensation nuclei
concentration.

@@

The main aim of this study is to evaluate the GSRM version of ICON. ICON
developed and maintained jointly by Deutscher Wetterdienst,
Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
Previous studies have identified substantial large-scale biases in climate
model clouds over the SO, affecting sea surface temperature and the Earth’s
albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
this region, particularly in light of the fact that subgrid-scale clouds and
convection are not parameterized in this model. This region is mostly dominated
by boundary layer clouds generated by shallow convection, and these are
problematic to observe by spaceborne lidars and radars, which are affected by
attenuation by overlapping and thick clouds and ground clutter, respectively.
Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are
nowoperational) are affected by the abovementioned issues, resulting in a
strong underestimation of cloud occurrence below 2 km relative to ground-based
lidar observations \citep{mcerlich2021}.  We hypothesise that this, in turn,
can lead to systematic biases in low clouds in climate models, which are
frequently evaluated against CloudSat--CALIPSO products. Reanalyses can also
suffer from cloud biases, as these are usually parametrised in their
atmospheric component, and also in regions where input observations are sparse.
This makes them a problematic reference for clouds over the SO, and any biases
relative to a reanalysis should be interpreted with caution. Instead, we chose
to use a large set of ship-based observations conducted with ceilometers and
lidars on board of the RV \emph{Polarstern} and other voyages and stations as a
reference for the model evaluation.

@@

The time period of ICON is relatively short, with only four full years of
simulation available. Moreover, the simulation is free-running, which means
that observations had to be temporally mapped to this time period (at the same
time relative to the start of the year) for the comparison. For these reasons,
one can expect the results to be slightly different due to reasons unrelated to
model biases, such as different weather conditions, partially accounted for by
the cyclone and stability subsetting, and the phase of climate oscillations
such as the ENSO in the observations and the model.

>>>>

The Southern Ocean (SO) is known to be a problematic region for climate model
biases \citep{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
surface and in situ observations and being a lower priority region for
numerical weather prediction (NWP) and climate model development because of its
distance from populated areas.  Nevertheless, radiation biases and changes over
an area of its size have a substantial influence on the global climate
\citep{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
and carbon uptake \citep{williams2023}, and the SO is an important part of the
global ocean conveyor belt \citep{wang2014}. In general, marine clouds have a
disproportionate effect on top of atmosphere (TOA) SW radiation due to the
relatively low albedo of the sea surface.  The relative longitudinal symmetry
of the SO means that model cloud biases tend to be similar across longitudes.

Here, we conventionally refer to the SO as ocean regions south of 40°S,
low-latitude SO as 40--55°S and high-latitude SO as south of 55°S. The reason
for this dividing latitude is to split the SO into about two equal zones, as
well as the results by \cite{schuddeboom2021} (Fig. 2b), showing a contrast in
CMIP model radiation biases, \cite{schuddeboom2019} (Fig. 2) and
\cite{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
Centre Global Environmental Model, and \cite{cesana2022} showing contrasting
cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
of \cite{niu2024}, however, support a different dividing line of 62°S based on
cloud condensation nuclei concentration.

@@

The main aim of this study is to evaluate the GSRM version of ICON. ICON
developed and maintained jointly by Deutscher Wetterdienst,
Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
Previous studies have identified substantial large-scale biases in climate
model clouds over the SO, affecting sea surface temperature and the Earth’s
albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
this region, particularly in light of the fact that subgrid-scale clouds and
convection are not parameterized in this model. This region is mostly dominated
by boundary layer clouds generated by shallow convection, and these are
problematic to observe by spaceborne lidars and radars, which are affected by
attenuation by overlapping and thick clouds \citep{mace2009,medeiros2010} and
ground clutter \citep{marchand2008}, respectively.  Specifically, the radar on
CloudSat and lidar on CALIPSO (neither of which are nowoperational) are
affected by the abovementioned issues, resulting in a strong underestimation of
cloud occurrence below 2 km relative to ground-based lidar observations
\citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to
systematic biases in low clouds in climate models, which are frequently
evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
cloud biases, as these are usually parametrised in their atmospheric component,
and also in regions where input observations are sparse.  This makes them a
problematic reference for clouds over the SO, and any biases relative to a
reanalysis should be interpreted with caution. Instead, we chose to use a large
set of ship-based observations conducted with ceilometers and lidars on board
of the RV \emph{Polarstern} and other voyages and stations as a reference for
the model evaluation.

@@

The time period of ICON is relatively short, with only four full years of
simulation available. Moreover, the simulation is free-running and
ocean-coupled, which means that observations had to be temporally mapped to
this time period (at the same time relative to the start of the year) for the
comparison. For these reasons, one can expect the results to be slightly
different due to reasons unrelated to model biases, such as different weather
conditions, partially accounted for by the cyclone and stability subsetting,
and the phase of climate oscillations such as the ENSO in the observations and
the model.
